Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-22 paper/tex/discussion.tex
more responses to Seth comments

The \trainz\ estimator of Section~\ref{sec:trainz}, which assigns every galaxy a \pzpdf\ equal to $N(z)$ of the training set, is introduced as an experimental control or null test to demonstrate this point via \textit{reductio ad absurdum}.
Because our training set is perfectly representative of the test set, $N(z)$ should be identical for both sets down to statistical noise.
\textbf{We make the alarming observation that \trainz, the experimental control, outperforms all codes on the CDF-based metrics, and all but one code on the $N(z)$ based statistics.}
The PIT and other CDF-based metrics upon which modern \pzpdf\ comparisons are built \citep{Bordoloi:10,Polsterer:16,Tanaka:17} can be gamed by a trivial estimator that yields only an affirmation of prior knowledge uninformed by the data.
In other words, such ensemble metrics are not appropriate for the task of selecting \pzpdf\ codes for analysis pipelines.
%\textit{Explain the connection between \trainz\ and these metrics.}

@@

This initial paper explores \pzpdf\ code performance in idealized conditions with perfect catalogue-based photometry and representative training data, but the resilience of each code to realistic imperfections in prior information has not yet been evaluated.
A top priority for a follow-up study is to test realistic forms of incomplete, erroneous, and non-representative template libraries and training sets as well as the impact of other forms of external priors that must be ingested by the codes, major concerns in \citet{Newman:2015, Masters:2017}.
Outright redshift failures due to emission line misidentification or noise spikes may be modeled by the inclusion of a small number of high-confidence yet false redshifts.
We plan to perform a full sensitivity analysis on a realistically incomplete training set of spectroscopic galaxies, modeling the performance of spectrographs, emission-line properties, and expected signal-to-noise to determine which potential training set galaxies are most likely to be excluded.

>>>>

The \trainz\ estimator of Section~\ref{sec:trainz}, which assigns every galaxy a \pzpdf\ equal to $N(z)$ of the training set, is introduced as an experimental control or null test to demonstrate this point via \textit{reductio ad absurdum}.
Because our training set is perfectly representative of the test set, $N(z)$ should be identical for both sets down to statistical noise.
\textbf{We make the alarming observation that \trainz, the experimental control, outperforms all codes on the CDF-based metrics, and all but one code on the $N(z)$ based statistics.}
The PIT and other CDF-based metrics upon which modern \pzpdf\ comparisons are built \citep{Bordoloi:10,Polsterer:16,Tanaka:17} can be gamed by a trivial estimator that yields only an affirmation of prior knowledge uninformed by the data.
In other words, such ensemble metrics are insufficient for the task of selecting \pzpdf\ codes for analysis pipelines.
%\textit{Explain the connection between \trainz\ and these metrics.}

@@

This initial paper explores \pzpdf\ code performance in idealized conditions with perfect catalogue-based photometry and representative training data, but the resilience of each code to realistic imperfections in prior information has not yet been evaluated.
A top priority for a follow-up study is to test realistic forms of incomplete, erroneous, and non-representative template libraries and training sets as well as the impact of other forms of external priors that must be ingested by the codes, major concerns in \citet{Newman:2015, Masters:2017}.
Outright redshift failures due to emission line misidentification or noise spikes may be modeled by the inclusion of a small number of high-confidence yet false redshifts.
We plan to perform a full sensitivity analysis on a realistically incomplete training set of spectroscopic galaxies, modeling the performance of spectrographs, emission-line properties, and expected signal-to-noise to determine which potential training set galaxies are most likely not to yield a secure redshift.

### 2019-11-22 paper/tex/results.tex
more responses to Seth comments

The histogram of PIT values, QQ plot, and QQ difference plot relative to the ideal diagonal are provided in Figure~\ref{fig:pitqq}, showcasing the biases and trends in the average accuracy of the \pzpdf s for each code.
The high QQ values (i.~e.~ more high than low PIT values) of \bpz, \cmnn, \delight, \eazy, and \gpz\ indicate \pzpdf s biased low, and the low QQ values (more low than high PIT values) of \skynet\ and \tpz\ indicate \pzpdf s biased high.
The gray shaded band marks the $2\sigma$ variance in PIT values found using the \trainz\ algorithm with a bootstrap resampling of the training set and a sample size of 30,000 galaxies, representing a very conservative estimate of the representative training sample size, and thus an approximate minimal error significance compared to ideal performance.
Deviations in the PIT histograms outside of this range show that significant biases are present for some codes.

>>>>

The histogram of PIT values, QQ plot, and QQ difference plot relative to the ideal diagonal are provided in Figure~\ref{fig:pitqq}, showcasing the biases and trends in the average accuracy of the \pzpdf s for each code.
The high QQ values (i.~e.~ more high than low PIT values) of \bpz, \cmnn, \delight, \eazy, and \gpz\ indicate \pzpdf s biased low, and the low QQ values (more low than high PIT values) of \skynet\ and \tpz\ indicate \pzpdf s biased high.
The gray shaded band marks the $2\sigma$ variance in PIT values found using the \trainz\ algorithm with a bootstrap resampling of the training set and a sample size of 30,000 galaxies, representing a very conservative estimate of the representative training sample size estimated as being required for direct \pz\ calibration \citep{Newman:2015}, and thus an approximate minimal error significance compared to ideal performance.
The existence of deviations in the PIT histograms outside of this gray shaded uncertainty range show that significant biases are present for some codes.
